%-------------------------
% Resume in Latex
% Author: Panambur Pawan Bhandarkar 
% License: MIT
%------------------------

\documentclass[letterpaper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries{}
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheadingWithoutTitle}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\textit{#1}} & \textit{\small #2} \\
    \end{tabular*}\vspace{-14pt}
}
\newcommand{\resumeSubheading}[4]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textbf{\textit{#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}



\newcommand{\shortSection}[1]{
    \vspace{-6pt}
    \section{#1}
}

\newcommand{\educationHeading}[5]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & {#2} \\
        \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}
    \small{\textbf{Courses : }{#5}}
}

\newcommand{\projectHeading}[3]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} 
        \hspace{-2pt} $\vert$ \hspace{-2pt} \small{\textit{#2}} 
        & 
        \textit{#3} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand*{\skill}[2]{
  \textbf{#1} : #2 \\
  \vspace{2pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{{\LARGE Panambur Pawan Bhandarkar}}\\
  Mountain View, CA & Portfolio:\href{https://www.bhandarkar.me/}{ \color{blue}{https://bhandarkar.me}} \\
  Email : \href{mailto:panambub@andrew.cmu.edu}{panambub@andrew.cmu.edu}   &   Github:\href{https://github.com/BhandarkarPawan}{ \color{blue}{https://github.com/BhandarkarPawan}}\\
  Mobile : +1-650-537-7341 &  Linkedin:\href{https://www.linkedin.com/in/bhandarkar/}{ \color{blue}{https://www.linkedin.com/in/bhandarkar}} \\

\end{tabular*}


%-----------SUMMARY-----------------
\shortSection {Summary}
\small Full-stack engineer experienced (2+ years) in building \textbf{responsive}, \textbf{accessible} web applications. I write \textbf{clean, modular}, and \textbf{well- tested} code that is easy for teams to \textbf{understand, extend}, and \textbf{integrate}. Seeking software engineering internship for Summer'23



%-----------EDUCATION-----------------
\shortSection{Education}
\educationHeading
{Carnegie Mellon University}{Mountain View, CA}
{Master of Science in Software Engineering; GPA: 4.0/4.0 }{Aug 2022 - Dec 2023}{
  Foundations of Software Engineering,
  Software Verification \& Testing,
  Software Requirements \& Interaction Design,
}

\vspace{5pt}

\educationHeading
{NMAM Institute of Technology }{Nitte, India}
{Bachelor of Computer Science;  GPA: 9.8/10 (top 1\%, Class of 2020) }{Jul 2016 - Apr 2020}{
  Data Structures \& Algorithms,
  Object Oriented Modelling \& Design,
  Linear Algebra \& Probability Theory
}


%-------- SKILLS------------
\shortSection{Skills}
\skill {Languages}{Typescript, JavaScript, Python, SQL, HTML, CSS, GraphQL}
\skill {Libraries \& Frameworks}{React, NodeJS, NextJS, Express, Redux, MongoDB, PostgreSQL, Flask, Bootstrap, TailwindCSS}
\skill {Tools }{Figma, Docker, AWS, S3, Postman, VSCode, Git, Miro, Jama}


%-----------EXPERIENCE-----------------
\shortSection{Experience}
\resumeSubheading
{Team AIBOD Inc.}{Fukuoka City, Japan}
{Software Engineer 2}{Nov 2021 - Apr 2022}
\vspace{2pt}
\resumeItemListStart
\resumeItemWithoutTitle{Developed \textbf{50+ UI components} with \textbf{React and TypeScript} resulting in a 10\% ($\sim$ 1.2M) increase in annual revenue.}
\resumeItemWithoutTitle{Created a \textbf{RESTful} payment server with a \textbf{microservice architecture} using \textbf{Python, Flask, and PostgreSQL}, expanding the customer base ($\sim$ ¥500K/year) to include BioPay users.}
\resumeItemWithoutTitle{\textbf{Containerized and deployed} applications using \textbf{Docker} and configured \textbf{AWS Cloudwatch} for remote monitoring, improving system performance across 15 customer locations.}
\resumeItemWithoutTitle{Trained and mentored interns and contract engineers in the company's stack.}

\resumeItemListEnd

\vspace{2pt}
\resumeSubheadingWithoutTitle
{Software Engineer 1}{Jul 2020 - Oct 2021}
\vspace{0pt}
\resumeItemListStart
\resumeItemWithoutTitle{Improved data pre-processing rate by 10x (from 20/h to 200/h) by \textbf{building image annotation tools with Python.} }
\resumeItemWithoutTitle{Designed and implemented a \textbf{GraphQL search system} with Apollo and Ariadne, streamlining 3 ongoing projects.}
\resumeItemWithoutTitle{Improved team efficiency and reliability with over 80\% code coverage through \textbf{unit and integration testing} with \textbf{Jest.}}
\resumeItemListEnd

\vspace{2pt}
\resumeSubheadingWithoutTitle
{AI Engineer Intern}{Feb 2020 - Jun 2020}
\vspace{0pt}
\resumeItemListStart
\resumeItemWithoutTitle{Fixed \textbf{20+ bugs} in the API server with \textbf{NodeJS and Typescript} and contributed to ongoing full-stack applications.}
\resumeItemWithoutTitle{Improved the accuracy of a \textbf{KNN-supervised classifier} from 80\% to 87\% through \textbf{feature engineering.}}
\resumeItemWithoutTitle{\textbf{Trained and evaluated} BERT NLP algorithm using \textbf{PyTorch} for Named Entity Recognition and integrated the AI backend and \textbf{Express API Server} to provide AI as a Service.}
\resumeItemListEnd

%-----------PROJECTS-----------------
\shortSection{Projects}
\projectHeading {Kanban Task Manager}{React, TypeScript, Styled-Components, Figma, Git}{Jun 2022 - Present}
\resumeItemListStart
\resumeItemWithoutTitle{Developed a highly \textbf{accessible} Kanban Task Manager with \textbf{pixel-perfect} implementation and best practices in \textbf{A11y, Semantic HTML, and ARIA labels}, which ensured usability with screen readers such as Apple Voice Over. Also generated clear API documentation with \textbf{API Blueprint} and \textbf{Postman}.}
\resumeItemListEnd

\vspace{4pt}
\projectHeading {Emergency Social Network}{HTML, CSS, Javascript, MongoDB}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Implemented a \textbf{robust system architecture}, applying SCRUM and Kanban agile practices to develop the app with a focus on usability. Applied \textbf{Object-Oriented Analysis \& Design} to lead development efforts and built a highly \textbf{maintainable, test-driven application} that provides \textbf{JSON-based RESTful APIs} for the frontend as well as headless clients}
\resumeItemListEnd

\vspace{4pt}
\projectHeading {Re:Use}{Figma, Jama, Miro}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Collaborated in a team of 6, to ideate a solution for problems faced by customers and volunteers in the donation industry by conducting \textbf{user research/interviews}, generating \textbf{storyboards} with Miro, \textbf{style guides} with Figma and a \textbf{Minimum-Viable-Product} (MVP) using React, Typescript and Styled-Components.}
\resumeItemListEnd

\vspace{4pt}
\projectHeading {Refriendo}{TypeScript, React, CSS, Figma, Git}{Oct 2021 - Jul 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Generated a \textbf{high-fidelity prototype} with a clean, visual design aesthetic and conducted \textbf{think-aloud usability testing} surveys to iteratively improve the design, followed by implementation of the mockups using a \textbf{Client-Server Architecture} and modern patterns such as \textbf{React Hooks} and \textbf{Context API}.}
\resumeItemListEnd

%-------- AWARDS------------
\shortSection{Awards \& Leadership}
\skill {Graduate Teaching Assistant}{Foundations of Software Engineering at Carnegie Mellon University}
\skill {Student Leader}{ ECE Graduate Organization at Carnegie Mellon University (Among 160 students).}
\skill {Youth Icon (title)}{Won first place in a national public speaking competition among 5000 participants in March 2019.}

\end{document}


